Measurement Bias from Address Aliasing

### 2014-05-25 paper.tex
Put borders around code listings

% See analysis for results showing this does not alias
\begin{figure}
  % [float=t, language=C, caption={Dynamically detect aliasing case, and avoid by pushing another stack frame.}, label={lst:loopfixed}, frame=lines]
  \begin{lstlisting}
  #define ALIAS(a, b) \
      (((long)&a) & 0xfff == ((long)&b) & 0xfff)
  static int i, j, k;
  int main() {
      int g = 0, inc = 1;
      if (ALIAS(inc, i) || ALIAS(g, i))
          return main();
      for (; g < 65536; g++) {
          i += inc;
          j += inc;
          k += inc;
      }
      return 0;
  }
  \end{lstlisting}
  \caption{Dynamically detect aliasing case, and avoid by pushing another stack frame.}
  \label{lst:loopfixed}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \lstinputlisting[
    language=C,
    %frame=lines
  ]{bin/convolution-kernel.c}
  \caption{Naive implementation of convolution, ignoring endpoints for simplicity. This program is highly sensitive to aliasing between input and output arrays.}
  \label{lst:conv}
\end{figure}

>>>>

% See analysis for results showing this does not alias
\begin{figure}
  \begin{lstlisting}[frame=single, xleftmargin=.1\textwidth, xrightmargin=.1\textwidth]
#define ALIAS(a, b) \
    (((long)&a) & 0xfff == ((long)&b) & 0xfff)
static int i, j, k;
int main() {
    int g = 0, inc = 1;
    if (ALIAS(inc, i) || ALIAS(g, i))
        return main();
    for (; g < 65536; g++) {
        i += inc;
        j += inc;
        k += inc;
    }
    return 0;
}
  \end{lstlisting}
  \caption{Dynamically detect aliasing case, and avoid by pushing another stack frame.}
  \label{lst:loopfixed}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \lstinputlisting[
    language=C,
    frame=single,
    xleftmargin=.1\textwidth,
    xrightmargin=.1\textwidth
  ]{bin/convolution-kernel.c}
  \caption{Naive implementation of convolution, ignoring endpoints for simplicity. This program is highly sensitive to aliasing between input and output arrays.}
  \label{lst:conv}
\end{figure}
